---
title       : "Are environmental and geographic variables effective surrogates for genetic variation in conservation planning?"
subtitle    : 
author      : Jeffrey O. Hanson
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Conserving genetic variation

```{r, include=FALSE}
### Initialization
## load packages
library(rworldxtra)
library(rgdal)
library(rgeos)
library(maptools)
library(RColorBrewer)
library(plyr)
library(dplyr)
library(ggplot2) # devtools::install_github('paleo13/ggplot2')
library(gridExtra)

## Load functions
for (x in dir(file.path('assets', 'functions'), full.names=TRUE)) source(x)

## load data
grid.sub.FPLY <- readRDS('assets/data/grid.sub.FPLY.rds')
scenario.PDF <- readRDS('assets/data/scenario.PDF.rds')
scenario.SDF <- readRDS('assets/data/scenario.SDF.rds')
grid.DF <- readRDS('assets/data/grid.DF.rds')
grid.FPLY <- readRDS('assets/data/grid.FPLY.rds')
grid.PLY <- readRDS('assets/data/grid.PLY.rds')
grid.PLY <- readRDS('assets/data/grid.PLY.rds')
spp.samples.DF <- readRDS('assets/data/spp.samples.DF.rds')

## create variables
# download basemap
data(countriesHigh)
countries.FPLY <- countriesHigh[
	countriesHigh$ADMIN %in% c(
		'Italy', 'Switzerland', 'France', 'Austria',
		'Germany', 'Slovenia', 'Croatia', 'Hungary',
		'Monaco', 'Germany', 'Slovakia', 'Czech Republic'
	)
,] %>% spFortify

# define ggplot2 color wheel function
gg_color_hue <- function(n) {
	hues <- seq(15, 375, length=n+1)
	hcl(h=hues, l=65, c=100)[1:n]
}
```

### Adaptive variation
* genetic variation that affects fitness
* caused by abiotic and biotic factors
* helps foster resilience to short-term environmental change

### Neutral variation
* genetic variation that *does not* affects fitness
* arises due to break-down in gene flow
* helps avoid inbreeding depression

# Typically prioritizations assume zero genetic variation within species: *can we use cheap variables as surrogates to make better decisions*?

--- .class #slide1

## Study area

```{r, message=FALSE, echo=FALSE, result="none", fig.align='center'}
for (x in dir(file.path('assets', 'functions'), full.names=TRUE)) source(x)
# calculate species richness
grid.PLY$Species_richness <- grid.PLY@data %>%
	select(5:(4+n_distinct(spp.samples.DF$species))) %>% as.matrix() %>% rowSums()

# plot species richness
ggplot() +
	geom_polygon(data=countries.FPLY, aes(x=long, y=lat, group=group),
		fill='grey85', color='grey70') +
	geom_polygon(data=spFortify(grid.PLY), aes(x=long, y=lat, 
		group=group, fill=Species_richness), color='grey10') +
	scale_fill_gradientn(name='Richness',
		colors=brewer.pal(9,'PuBu'),
		guide=guide_colorbar(ticks=element_line(color='black'), border=element_line(color='black'))
	) +
	theme_classic() +
	theme(
		axis.ticks=element_blank(), axis.text=element_blank(), axis.line=element_blank(), plot.margin = unit(c(0, 0, 0, 0), "lines"), axis.title=element_blank(),
		panel.border=element_rect(color='black', fill=NA, size=1), legend.title=element_text(size=25)
	) +
	coord_cartesian(
		xlim=buffered.range(grid.FPLY$long, 0),
		ylim=buffered.range(grid.FPLY$lat, 0)
	)
```

--- .class #slide2

## Climatic variation

```{r, message=FALSE, echo=FALSE, result="none", fig.align='center', fig.width=14, fig.height=7}
for (x in dir(file.path('assets', 'functions'), full.names=TRUE)) source(x)
do.call(
	grid.arrange,
		append(
		llply(grep('^env\\_.*$', names(grid.DF), value=TRUE), function(x) {
			grid.FPLY$plot_title <- paste0('PC ', substr(x, nchar(x), nchar(x)))
			ggplot() +
				geom_polygon(data=countries.FPLY, aes(x=long, y=lat, group=group),
					fill='grey85', color='grey70') +
				geom_polygon(data=grid.FPLY, aes_string(x='long', y='lat', 
					group='group', fill=x), color='grey10') +
				theme_classic() +
				theme(
					axis.ticks=element_blank(), axis.text=element_blank(), axis.line=element_blank(), plot.margin = unit(c(0, 0, 0, 0), "lines"),
					axis.title=element_blank(),
					panel.border=element_rect(color='black', fill=NA, size=1),
					strip.background = element_rect(fill='grey20'),
					strip.text = element_text(color='white', size=30)
				) +
				coord_cartesian(
					xlim=buffered.range(grid.FPLY$long, 0),
					ylim=buffered.range(grid.FPLY$lat, 0)
				) +
				scale_fill_gradientn(name='',
					colors=brewer.pal(9, 'RdYlBu'),
					guide=guide_colorbar(ticks=element_line(color='black'), border=element_line(color='black'))
				) +
				facet_wrap(~ plot_title)
		}),
		list(ncol=3)
	)
)
```

--- .class #slide3

## Preliminary results: prioritisations

```{r, message=FALSE, echo=FALSE, result="none", fig.align='center', fig.width=14, fig.height=7}
## make maps
for (x in dir(file.path('assets', 'functions'), full.names=TRUE)) source(x)
# filter data
grid.sub.FPLY <- filter(grid.sub.FPLY, Context=='Multi-species\n(equal costs)')
# make plot
ggplot() +
	geom_polygon(data=countries.FPLY, aes(x=long, y=lat, group=group),
		fill='grey85', color='grey70') +
	geom_polygon(data=grid.sub.FPLY, aes_string(x='long', y='lat', 
		group='group', fill='Selection.Frequency'),
		alpha=0.8, color='grey10') +
	theme_classic() +
	theme(axis.ticks=element_blank(), axis.text=element_blank(),
		plot.margin=unit(c(0,0,0,0),'cm'), axis.line=element_blank(),
		strip.background = element_rect(fill='grey20'),
		strip.text = element_text(color='white', size=30),
		legend.position='bottom', legend.key.width=unit(1.8, 'cm'),
		legend.title=element_text(vjust=-5, size=25),
		legend.margin=unit(c(0.1), 'cm'),
		axis.title=element_blank()) +
	coord_cartesian(
		xlim=buffered.range(grid.sub.FPLY$long, 0),
		ylim=buffered.range(grid.sub.FPLY$lat, 0)
	) +
	facet_wrap( ~ Prioritization) +
	scale_fill_gradientn(name='Selection Frequency (%)',
		colors=brewer.pal(9, 'PuBu'),
		guide=guide_colorbar(title.position='bottom', title.hjust=0.5,
			ticks=element_line(color='black'), border=element_line(color='black'))
	)
```

--- .class #slide4

## Preliminary results: performance

```{r, message=FALSE, echo=FALSE, warn=FALSE, result="none", fig.align='center', fig.width=14, fig.height=7}
## make barplot
for (x in dir(file.path('assets', 'functions'), full.names=TRUE)) source(x)
# filter data
scenario.SDF <- filter(scenario.SDF, Context=='Multi-species\n(equal costs)', !is.na(genetic.held))
# make plot
suppressWarnings({
	ggplot(aes(x=Prioritisation,y=genetic.held),
		data=scenario.SDF) +
		geom_boxplot(position=position_dodge(0.9)) +
		scale_fill_manual(name='Prioritisation',
			values=c('grey80','grey50','grey20')) +
		ylab('Genetic variation secured (%)') +
		xlab('') +
		scale_y_continuous(breaks=c(0,0.25,0.5,0.75,1), limits=c(NA, 1.2)) +
		theme_classic() +
		theme(strip.background = element_rect(fill='grey20'),
			strip.text = element_text(color='white', size=30),
			panel.border = element_rect(color='black', fill=NA),
			axis.text.x=element_text(angle=45, hjust=1, vjust=1, size=25),
			axis.title=element_text(size=20), axis.text.y=element_text(size=20)) +
		facet_wrap( ~ Metric)
})
```

--- .class #slide5

